paper figures

### 2025-08-01 paper_figures.Rmd
update for revision

```{r Fig3G, fig.width=1.25 * fig_scale, fig.height=3.5 * fig_scale}
train_batches <- c('20220`4`25','20221118','20221212','20230120','20230213')
test_batches <- '20240830'
train <- CH12.meta$Batch %in% train_batches
test <- CH12.meta$Batch %in% test_batches

>>>>

```{r Fig3G, fig.width=1.25 * fig_scale, fig.height=3.5 * fig_scale}
train_batches <- c('20220425','20221118','20221212','20230120','20230213')
test_batches <- '20240830'
train <- CH12.meta$Batch %in% train_batches
test <- CH12.meta$Batch %in% test_batches
